Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-01 paper/paper.Rmd
finished review of student coding decisions
Initial analysis in paper

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(dplyr)
library(xtable)
```

@@

```{r, results='asis'}
project_plan_raw <- read_csv("data/planning_and_outcomes.csv")

@@

What’s the subjective “replication rating” given by MCF, ES, and RH? Criterion is based on the theoretical interpretation of the original finding. (0 = non-replication, .5 is substantial hints of the same pattern or a significant but different pattern, 1 = full replication).

```{r}
mean(d$replicated_TA)
```

```{r}
mean(d$replicated_student, na.rm=TRUE)
```

@@

@@

@@

```{r}
d %>% 
  group_by(fidelity) %>%
  summarise(replicated = mean(replicated_TA))
```

@@

```{r}
layout(matrix(1:22,nr=11,byr=T))
for (key in project_plan$project_key) {
  tryCatch(source(function() {
  orig <- readPNG(paste0("figures/",key,"-original.png"))
  rep <- readPNG(paste0("figures/",key,"-replication.png"))
  plot(orig)
  plot(rep)}
  ))
}
```

>>>>

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(dplyr)
library(xtable)
library(readr)
library(ggplot2)
```

@@

```{r, results='asis'}
setwd("~/replication_project")
project_plan_raw <- read_csv("data/planning_and_outcomes.csv")

@@

Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication. Criterion is based on the theoretical interpretation of the original finding. (0 = non-replication, .5 is substantial hints of the same pattern or a significant but different pattern, 1 = full replication). We find that the these ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students was `r mean(d$replicated_TA, na.rm=TRUE)` and `r mean(d$replicated_student, na.rm=TRUE)` respectively.

Flag: waiting for one student's subjective rating
```{r}
table(d$replicated_TA,d$replicated_student) # Make prettier
```

@@

```{r, echo=F}
d$original_p_value_bins <- NA
d$original_p_value_bins[d$original_p_value %in% c("<.05","0.04")] <- "<.05"
d$original_p_value_bins[d$original_p_value %in% c("0.007","0.001")] <- "<.01"
d$original_p_value_bins[d$original_p_value %in% c("<.001","< .001")] <- "<.001"
d$rep_p_value_05 <- d$rep_p_value < .05
```

We assess the replication p-value to determine whether the key statistic found a significant effect at the traditional p=.05 level. We find this to be true for only `r sum(d$rep_p_value_05)` of the studies. However, the well-documented "dance of the p-values" [@cummings2011] suggests that the inference drawn from a single replication p-value may not be highly informative, and other metrics suchs as the confidence interval and Bayes factor analysis below can give the reader a better understanding of replication success.

Flag: Are all effects in the hypothesized direction?

```{r}
ggplot(d,aes(x=original_p_value_bins,y=rep_p_value, color=as.factor(d$replicated_TA))) +
  geom_jitter(height=0, width=.4) +
  theme_bw() + 
  geom_hline(yintercept=c(0.05,0.1,0.2), color="gray")
```

@@

We determine whether the original reported effect size is included in the 95\% confidence interval found in the replication studies.

Flag: Original effect size not given for auc?
```{r}
d$original_ES <- as.numeric(gsub(".*=(.*)","\\1", d$original_ES_text))
#Ensure that effect size is given in same units... Make beautiful ci chart here...

```

@@

```{r,eval=F}
d$high_fidelity <- d$replication_fidelity_MCF > median(d$replication_fidelity_MCF)
d %>%
  group_by(high_fidelity) %>%
  summarise(replicated = mean(replicated_TA))
```

@@

```{r, eval=F}
layout(matrix(1:22,nr=11,byr=T))
for (key in project_plan$project_key) {
  tryCatch(source(function() {
  orig <- readPNG(paste0("figures/",key,"-original.png"))
  rep <- readPNG(paste0("figures/",key,"-replication.png"))
  plot(orig)
  plot(rep)}
  ))
}
```
